Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Selective replay of km's changes
notation
some references

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\nv}[1]{[{\color{cyan}#1 --- Nikos}]}
\newcommand{\kk}[1]{[{\color{magenta}#1 --- kk}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report

@@

Nodes $f$ of the graph represent functions from one (possibly empty)
input stream to an output stream $f : D^* \rightarrow D^*$. $D$
represents the basic data type of a line of characters. This
representation captures the majority of shell commands. The nodes are
monotonic, meaning that they cannot retract their output. More
formally, $\forall f, x, y, f(x) = y$, then for any $x'$, there exists
$y'$ such that $f(x.x') = y.y'$, where $.$ is standard concatenation
and will be omitted when obvious. An example of a node is the
following command:

@@

>>>>

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\nv}[1]{[{\color{cyan}#1 --- nv}]}
\newcommand{\kk}[1]{[{\color{magenta}#1 --- kk}]}
\newcommand{\km}[1]{[{\color{blue}#1 --- km}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report

\newcommand{\kstar}{^{\textstyle *}}

@@

Nodes $f$ of the graph represent functions from one (possibly empty)
input stream to an output stream $f : D\kstar \to D\kstar$. $D$
represents the basic data type of a line of characters. This
representation captures the majority of shell commands. The nodes are
monotonic, meaning that they cannot retract their output. More
formally, $\forall f, x, y, f(x) = y$, then for any $x'$, there exists
$y'$ such that $f(x.x') = y.y'$, where $.$ is standard concatenation
and will be omitted when obvious. An example of a node is the
following command:

@@

\cite{HSSGG2014, SHGW2015} discuss optimizing transformations, but their correctness is established using informal arguments based on operational intution.

The paper \cite{MSAIT2019} proposes a denotational semantic framework for stream processing where the data streams are seen as partial orders, and establishes the soundness of some common parallelizing transformations on dataflow graphs.
